Plotting cropland biases

### 2015-06-24 Rmd/compare-landcover.Rmd
Many changes made, some revisions to existing Rmds, but main work done was to create magisterial-district-bias.Rmd and associated figures.

```{r, eval = FALSE}
salc <- raster(full_path(p_data, "sa_ag_masked.tif")) * 100
globsa_list_sum <- lapply(full_path(p_data, dir(p_data, "globSA*.*1kmrect_sum.tif")[c(2:3, 1)]), raster)
fnames <- full_path(p_data, dir(p_data, "mod_1*.*1kmrect_sum.tif")[c(2:3, 1)])
modsa_list_sum <- lapply(fnames, raster)
glcsa <- raster(full_path(p_data, "glcsa_masked.tif"))
geow <- raster(full_path(p_data, "geowikisa_masked.tif"))
lclist <- c(salc, globsa_list_sum, modsa_list_sum, glcsa, geow)  # into list
names(lclist) <- c("sa30", "globmin", "globmu", "globmax", "modmin", "modmu",
                   "modmax", "glcsh", "geow")
```

>>>>

```{r, eval = FALSE}
salc <- raster(full_path(p_data, "sa_ag_masked.tif")) * 100
ds <- full_path(p_data, dir(p_data, "globSA*.*1kmrect_sum.tif")[c(2:3, 1)])
globsa_list_sum <- lapply(ds, raster)
fnames <- full_path(p_data, dir(p_data, "mod_1*.*1kmrect_sum.tif")[c(2:3, 1)])
modsa_list_sum <- lapply(fnames, raster)
glcsa <- raster(full_path(p_data, "glcsa_masked.tif"))
geow <- raster(full_path(p_data, "geowikisa_masked.tif"))
lclist <- c(salc, globsa_list_sum, modsa_list_sum, glcsa, geow)  # into list
names(lclist) <- c("sa30", "globmin", "globmu", "globmax", "modmin", "modmu",
                   "modmax", "glcsh", "geow")
```

### 2015-06-24 Rmd/landcover-bias-plots.Rmd
Many changes made, some revisions to existing Rmds, but main work done was to create magisterial-district-bias.Rmd and associated figures.

# DF <- do.call(rbind.data.frame, lapply(snms[-2], function(x) {
#   dstats_all[[2]][[x]]$f25[, c(1, 8)]
# }))
# dlm <- lm(mu ~ poly(V1, degree = 2), data = DF)
# plot(DF[, 1], DF[, 2])
# lines(predict.lm(dlm, newdata = data.frame("V1" = 1:100)))

# for(bt in 1:2) {
#   pdf(full_path(p_fig, btype[bt]), width = 7, height = 7)
#   lmat <- rbind(m, m3)
#   l <- layout(lmat)
#   par(mar = c(3, 0, 0, 0), oma = c(3, 4, 2, 2))
#   snms <- names(dstats_all[[bt]])[names(dstats_all[[bt]]) != "glcsh"]
#   dset <- dstats_all[[bt]][snms]
#   for(i in 1:length(snms)) { i
#     #bt <- 1
#     d <- dset[[snms[i]]]$f1
#     n <- nrow(d)
#     plot(pp$x, pp$y, ylim = pp$yl[[bt]], xlim = pp$xl, type = "l", 
#          lwd = pp$y1lwd[[bt]], axes = FALSE, 
#          xlab = "", ylab = "")
#     if(i == 1) axis(2, at = pp$yax1[[bt]], labels = pp$yax1[[bt]], las = 2, 
#                     mgp = c(1, 0.6, 0))
#     axis(1, at = 1:20, labels = pp$xaxl, las = 2, mgp = c(1, 0.4, 0), 
#          tcl = -0.3, pos = pp$yaxp[[bt]], cex = 0.8)
#     for(z in 1:length(pp$y2[[bt]])) {
#       lines(pp$x, rep(pp$y2[[bt]][z], 2), lwd =pp$y2lwd, col = pp$y2lc[[bt]][z])
#     }
#     for(k in 1:n) {
#       a <- seq(grep("2.5", colnames(d)), by = 1, length.out = 6)
#       if(!is.na(d[k, 2])) {
#         boxplot_v(k, d[k, a], n, 150, 10, bcol, fcol, pcex = 0.5, 
#                   lwd = c(1, 0.5, 2))
#       }
#     }
#     lines(1:n, d[, "mu"], pch = 20, col = cols[i], lwd = 3)
#     if(i == 1) mtext(ifelse(bt == 1, "% bias", "% bias (absolute)"), side = 2, 
#                      line = 2.2, cex = 0.8)
#     mtext(lcnms[i], side = 3, line = 0, col = cols[i])
#   }
#   mtext("% cropland", side = 1, outer = TRUE, line = -36.7, cex = 0.8)
#   par(mar = c(0.5, 0, 0.5, 0.3))
#   for(i in 1:length(snms)) {
#     highcounter <- rep(0, length(lev))
#     for(j in 1:length(lev)) {
#       plot(pp$x, pp$y, ylim = pp$yl2[[bt]], xlim = pp$xl, type = "l", lwd = 1, 
#            axes = FALSE, xlab = "", ylab = "", xaxs = "i")
#       for(z in 1:length(pp$y2[[bt]])) {
#         lines(pp$x, rep(pp$y2[[bt]][z], 2), lwd = pp$y2lwd, 
#               col = pp$y2lc[[bt]][z])
#       }
#       d <- dset[[i]][[lev[j]]]
#       n <- nrow(d)
#       lines(1:n, d[, "mu"], pch = 20, col = cols[i], lwd = pp$y3lwd[j])
#       muv <- round(mean(d[, 8], na.rm = TRUE))
#       if(j == length(lev)) {
#         mtext(expression(mu), side = 1, cex = 0.8, col = "grey10", 
#               line = ifelse(bt == 1, -1.5, -1.8), adj = 1.1)
#       }
#       text(10, pp$yl2[[bt]][1] + 10, labels = muv, cex = 1.3, col = "grey10")
#       toohigh <- which(d[, "mu"] > pp$yl2[[bt]][2])
#       if(length(toohigh) > 0) {
#         highcounter[j] <- 1
#         xi <- toohigh[which.max(d[toohigh, "mu"])]
#         text(xi, y = pp$yl2[[bt]][2], labels = round(d[xi, "mu"]), 
#              col = "grey50", xpd = NA)
#       }
#       if(j == length(lev)) {
#         if(sum(highcounter) > 0) {
#           mtext("max", side = 3, cex = 0.7, col = "grey50", line = -0.7, 
#                 adj = 1.1)
#         }
#       }
#       if(j == 1) {
#         axis(2, at = seq(pp$yl2[[bt]][1], pp$yl2[[bt]][2], 10), 
#              labels = pp$yax2[[bt]], las = 2, mgp = c(1, 0.6, 0))
#       }
#       if(i == 1) mtext(levnms[j], side = 3, line = -0.4, cex = 0.8)
#       axis(1, at = c(1, 5, 10, 15, 20), labels = rep("", 5), mgp = c(1, 1, 0), 
#            tcl = -0.7, lwd.ticks = 1.2, pos = pp$yl2[[bt]][1])
#       axis(1, at = 1:20, labels = rep("", 20), las = 2, mgp = c(1, 0.4, 0), 
#            tcl = -0.3, pos = pp$yl2[[bt]][1])
#       if(i == length(snms)) {
#         axis(1, at = 1:20, labels = pp$xaxl2, las = 2, mgp = c(1, 0.8, 0), 
#              tcl = -0.3, pos = pp$yl2[[bt]][1])
#       }
#     }
#   }
#   mtext(ifelse(bt == 1, "% bias", "% bias (absolute)"), side = 2, line = 2.2, 
#         cex = 0.8, outer = TRUE, adj = 0.35)
#   mtext("% cropland", side = 1, outer = TRUE, line = 1.5, cex = 0.8)
#   dev.off()
# }

#   for(j in 1:6) { #j <- 1
#     plot(pp$x, pp$y, ylim = pp$yl, xlim = pp$xl, type = "l", lwd = 2, axes = FALSE, xlab = "", ylab = "")
#     for(z in 1:length(pp$y2)) {
#       for(q in pp$x21) lines(q, rep(pp$y2[z], 2), lwd = pp$y2lwd[z], col = pp$ycol)
#     }
#     if(i == 1) axis(2, at = seq(-100, 100, 50), labels = seq(-100, 100, 50), las = 2)
#     #if(i != 1) axis(2, at = seq(-100, 100, 50), labels = rep("", 5))
#     if(j == 6) axis(1, at = 1:20, labels = lvec, las = 2, mgp = c(1, 0.7, 0), tcl = -0.3)
#     df <- d[[j]]
#     for(k in 2:n) {
#       a <- seq(grep("2.5", colnames(df)), by = 1, length.out = 6)
#       if(!is.na(df[k, 2])) boxplot_v(k, df[k, a], n, 150, 10, bcol, fcol, pcex = 0.5, lwd = c(1, 0.5, 2))
#       if(!is.na(df[k, 7])) lines(1:19, df[-20, "mu"], pch = 20, col = cols[i], lwd = 1.5)
#     }
#     print(mean(df[, 8], na.rm = TRUE))
#   }
# }
# dev.off()

```

>>>>

DF <- do.call(rbind.data.frame, lapply(snms[4], function(x) {
  dstats_all[[2]][[x]]$f1[, c(1, 8)]
}))
dlm <- lm(mu ~ poly(V1, degree = 2), data = DF)
plot(DF[, 1], DF[, 2])
lines(predict.lm(dlm, newdata = data.frame("V1" = 1:110)))
```
